Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2015-02-01 draft_lm1.tex
fixed code for labels of fig3. Closes #13

\bibliography{lm1}
\section*{Figure Legends}
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{plots/concat_SI.png}
\end{center}
\caption{
{\bf Susceptibles and Infectious posterior curves.}  The curves were estimated 
only for the periods where $R_t> 1$.  The susceptible curves in the top panel 
reflect the prevalence of fraction of susceptibles to circulating strain(s) for 
each epidemic/outbreak. In the lower panel see the posterior distribution 
of infectious curves, represented by its Median and 95\% credible interval. The 
credible intervals are very narrow, and can be hard to distinguish from the 
median line. 
Scatter plot shows the observed cases. Prevalences are scaled as fractions 
of the entire population.
}
\label{Fig:S0}
\end{figure}

>>>>

\bibliography{lm1}
\section*{Figure Legends}
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{plots/concat_SI.png}
\end{center}
\caption{
{\bf Susceptibles and Infectious posterior curves.}  The curves were estimated 
only for the periods where $R_t> 1$.  The susceptible curves in the top panel 
reflect the prevalence of fraction of susceptibles to circulating strain(s) for 
each epidemic/outbreak. In the lower panel, we see the posterior distribution 
of infectious curves, represented by its Median and 95\% credible interval. The 
credible intervals are very narrow, and can be hard to distinguish from the 
median line. 
Scatter plot shows the observed cases. Prevalences (y-axes) are scaled as 
fractions of the entire population.
}
\label{Fig:S0}
\end{figure}
